Limma Tutorial

### 2018-04-13 VirusHoneyBee/DESeq2/makeDataMetrics.Rmd
Finsh 27 sets of DEG counts

    RDV <- metrics[which(metrics[which(metrics$padj <0.05),]$log2FoldChange>0),]$ID
    RDN <- metrics[which(metrics[which(metrics$padj <0.05),]$log2FoldChange<0),]$ID
    RD_VIRUS <- metrics[which(metrics$padj <0.05),]$ID
    saveRDS(RDV, file="RDV.Rds")
    saveRDS(RDN, file="RDN.Rds")
    saveRDS(RD_VIRUS, file="RD_VIRUS.Rds")

>>>>

    GDC1 <- metrics[which(metrics[which(metrics$padj <0.05),]$log2FoldChange>0),]$ID
    GDV1 <- metrics[which(metrics[which(metrics$padj <0.05),]$log2FoldChange<0),]$ID
    GD_VIRUS1 <- metrics[which(metrics$padj <0.05),]$ID

    GDV <- unname(sapply(GDV1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))
    GDC <- unname(sapply(GDC1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))
    GD_VIRUS <- unname(sapply(GD_VIRUS1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))

    saveRDS(GDV, file="GDV.Rds")
    saveRDS(GDC, file="GDC.Rds")
    saveRDS(GD_VIRUS, file="GD_VIRUS.Rds")

### 2018-04-13 VirusHoneyBee/EdgeR/edgeR/makeDataMetrics.Rmd
Finsh 27 sets of DEG counts

>>>>

    GEC1 <- rownames(lrt5[which(lrt5$logFC>0),])
    GEV1 <- rownames(lrt5[which(lrt5$logFC<0),])
    GE_VIRUS1 <- rownames(lrt5)

    GEC <- unname(sapply(GEC1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))
    GEV <- unname(sapply(GEV1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))
    GE_VIRUS <- unname(sapply(GE_VIRUS1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))

    saveRDS(GEC, file="GEC.Rds")
    saveRDS(GEV, file="GEV.Rds")
    saveRDS(GE_VIRUS, file="GE_VIRUS.Rds")

### 2018-04-13 VirusHoneyBee/LimmaVoom/makeDataMetrics.Rmd
Finsh 27 sets of DEG counts

```{r}
summary(decideTests(efit))
```

>>>>

```{r}
summary(decideTests(efit))

countDF <- as.data.frame(decideTests(efit)@.Data)
GLC1 <- rownames(countDF)[which(countDF==1)]
GLV1 <- rownames(countDF)[which(countDF==-1)]
GL_VIRUS1 <- c(GLC1, GLV1)

GLC <- unname(sapply(GLC1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))
GLV <- unname(sapply(GLV1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))
GL_VIRUS <- unname(sapply(GL_VIRUS1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))

saveRDS(GLC, file="GLC.Rds")
saveRDS(GLV, file="GLV.Rds")
saveRDS(GL_VIRUS, file="GL_VIRUS.Rds")

```
